---
title: "AFL Wednesday Wonk 1 - The Draw"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Wednesday Wonk 1

Our initial Wednesday Wonk Topic is a topical one after Round 4 - the Draw! 

A lot of chat this week about whether the draw should be kept in the AFL. There are lots of arguments to be had but there is also data! 

This week we are asking you specifically to "mount an argument either for or against the draw using data".

There is no right or wrong answer and lots of angles to attack this from

## Data
For those wanting the historical results of the AFL, you can use `fitzRoy` in R using the following code. 

```{r data}
library(fitzRoy)
results <- get_match_results()

head(results)
```

If you don't use R and just want a csv - find that [here](https://github.com/jimmyday12/aflwonkwednesday/blob/master/data/wonk1_match_results.csv). 

All data is courtesy of [afltables](afltables.com) so please acknowledge appropriately. 

### Submission
There is no formal submission process. Just make sure you share you responses in the AFL Wonk Slack group, on Twitter (using the #AFLWonkWednesday hashtag) and/or, for those that way inclined, on your own blogs.